Franchak_ReAnalysis

### 2020-08-11 analysis-franchak/franchak_reanalysis.Rmd
Update franchak re-analysis with new pipeline

# Preprocessing
## Libraries
```{r}
rm(list=ls()) # remove all objects from current workspace
library(ggthemes)
library(langcog)
library(tidyverse)
library(cowplot)

@@

## Read in detections and merge with subid from above
```{r}
detections <- read.csv('../data/franchak_dataset/openpose_detections/franchak_frames_openpose_master_frames.csv') 
dets <- detections %>%
  left_join(filenames) %>%
  mutate(sub_id = as.factor(sub_id))
```

# Merge detections with position data (should merge on subid, frame)
```{r}
pos_detections  <- all_pos_data %>%
  left_join(dets) 
```

@@

@@

### Save out preprocessed data
```{r}
save(file = '../data/franchak_dataset/preprocessed/franchak_dataset_detections.RData', pos_detections)
```

# Basic analyses
## Compute faces by infant posture
```{r}
faces_by_pos  <- pos_detections %>%
  group_by(sub_id, infant_posture_label) %>%
  summarize(prop_faces = mean(face_openpose)) %>%
  group_by(infant_posture_label) %>%
  multi_boot_standard(col = 'prop_faces')

@@

(ggplot(faces_by_CG_pos, aes(x=caregiver_posture_label, y=mean, col=caregiver_posture_label)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  theme_few())
```

@@

### Plot hands by infant posture
```{r}
(hands_by_pos_plot <- ggplot(hands_by_pos, aes(x=infant_posture_label, y=mean, col=infant_posture_label)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_point(data=hands_by_pos_by_sub, aes(x=infant_posture_label, y=prop_faces, col=infant_posture_label), alpha=.2) +
  theme_few(base_size=18) +
  ylab('Prop hands detected') +
   xlab('Infant posture') + 
  ylim(c(0,.4)) +
  theme(legend.position = 'none') +
  scale_color_manual(name = "Posture", values=c("#339966","#eb7928","#0099cc")))
)

>>>>

# Preprocessing
## Libraries
```{r}
rm(list=ls()) # remove all objects from current workspace
library(ggthemes)
library(langcog)
library(tidyverse)
library(cowplot)
```

@@

## How much data do we have for each subject?
```{r}
(frames_by_sub <- all_pos_data %>%
  group_by(sub_id) %>%
  summarize(num_frames = length(unique(frame))) %>%
  kable())
```

## Read in detections and merge with subid from above
```{r}
csv_dir = paste0(here::here(),'/data/franchak_dataset/openpose_detections/csvs_compressed_with_conf/')
files = dir(csv_dir)
sub_count = 0

for (f in files){
  print(f)
  sub_count = sub_count + 1
  print(sub_count)
  this_sub <- read.csv(paste0(csv_dir,f)) %>%
    as.tibble()

  if (sub_count==1){
     detections <- this_sub
  } else{
  detections <- detections %>%
    full_join(this_sub) 
  }
}

dets <- detections %>%
  mutate(vid_name = str_split_fixed(subid,'.json',2)[,1]) %>%
  select(-subid) %>%
  left_join(filenames) %>%
  mutate(sub_id = as.factor(sub_id)) %>%
  rename(frame = frame_num)

# Merge detections with position data (should merge on subid, frame)
```{r}
pos_detections  <- all_pos_data %>%
  left_join(dets, by=c('frame','sub_id')) 
```

@@

pos_detections <- pos_detections %>%
  mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose))

@@

### Save out preprocessed data
```{r}
# save(file = '../data/franchak_dataset/preprocessed/franchak_dataset_detections_july2020.RData', detections)
save(file = '../data/franchak_dataset/preprocessed/franchak_dataset_detections_by_posture_july2020.RData', pos_detections)

# Basic analyses
## Compute faces by infant posture
```{r}
faces_by_pos  <- pos_detections %>%
  group_by(sub_id, infant_posture_label) %>%
  dplyr::summarize(prop_faces = mean(face_openpose)) %>%
  group_by(infant_posture_label) %>%
  multi_boot_standard(col = 'prop_faces')

@@

(ggplot(faces_by_CG_pos, aes(x=caregiver_posture_label, y=mean, col=caregiver_posture_label)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  theme_few())

@@

```{r}
faces_by_both_pos  <- pos_detections %>%
  group_by(sub_id, infant_posture_label, caregiver_posture_label) %>%
  summarize(prop_faces = mean(face_openpose)) %>%
  group_by(infant_posture_label,caregiver_posture_label) %>%
  multi_boot_standard(col = 'prop_faces')

(ggplot(faces_by_both_pos, aes(x=infant_posture_label, y=mean)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  theme_few() +
  facet_wrap(~caregiver_posture_label))

### Plot hands by infant posture
```{r}
(hands_by_pos_plot <- ggplot(hands_by_pos, aes(x=infant_posture_label, y=mean, col=infant_posture_label)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_point(data=hands_by_pos_by_sub, aes(x=infant_posture_label, y=prop_hands, col=infant_posture_label), alpha=.2) +
  theme_few(base_size=18) +
  ylab('Prop hands detected') +
   xlab('Infant posture') + 
  ylim(c(0,.4)) +
  theme(legend.position = 'none') +
  scale_color_manual(name = "Posture", values=c("#339966","#eb7928","#0099cc")))
